Job Demands-Resources model components through the lens of O*NET classifications

### 2023-01-28 Submission.Rmd
6 graphs into 2 figures

topresource <- head(sortresource, 10)

@@

ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed Upon as a Resource") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

topchallenge <- head(sortchallenge, 10)

@@

ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

tophindrance <- head(sorthindrance, 10)

@@

ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

Figures \@ref(fig:resourcesagree), \@ref(fig:challengesagree), and \@ref(fig:hindrancesagree) present the resources, challenges, and hindrances that are *largely agreed on* as indexed by (relatively) low standard deviations.[^caveat]

@@

As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered *hindrances*, with the 10 elements showing the greatest agreement still ranging in standard deviations from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`. What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 10 resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 10 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`.

@@

topresource <- head(sortresource, 10)

@@

ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Resource") + 
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

topchallenge <- head(sortchallenge, 10)

@@

ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

tophindrance <- head(sorthindrance, 10)

@@

ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

Figures \@ref(fig:resourcesdisagree), \@ref(fig:challengesdisagree), and \@ref(fig:hindrancesdisagree) present the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).

>>>>

topresource <- head(sortresource, 8)    ## changed for combined plot (1/28/23)

@@

a <- ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed Upon as a Resource") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

topchallenge <- head(sortchallenge, 8)    ## changed for combined plot (1/28/23)

@@

b <- ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

tophindrance <- head(sorthindrance, 8)  ## changed for combined plot (1/28/23)

@@

c <- ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

Figure \@ref(fig:combinegraphs) presents resources, challenges, and hindrances that are *largely agreed on* as indexed by (relatively) low standard deviations.[^caveat] There are only 8 characteristics presented per perceived category because of limited space. All sortable ratings are available in the online resources.

@@

```{r combinegraphs, fig.cap="Characteristics percieved most similarly (lowest standard deviations).", fig.height=10}

library(gridExtra)
grid.arrange(a, b, c, nrow = 3)

As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered *hindrances*, with the 8 elements showing the greatest agreement still ranging in standard deviations from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`. What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 8 resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`.

@@

topresource <- head(sortresource, 8)

@@

d <- ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Resource") + 
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

topchallenge <- head(sortchallenge, 8)

@@

e <- ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

tophindrance <- head(sorthindrance, 8)

@@

f <- ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

```{r combinegraphs2, fig.cap="Characteristics percieved most *DIS*similarly (lowest standard deviations).", fig.height=10}

library(gridExtra)
grid.arrange(d, e, f, nrow = 3)

Figure \@ref(fig:combinegraphs2) presents the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating).

### 2023-01-28 Submission.tex
6 graphs into 2 figures

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/resourcesagree-1.pdf}
\caption{\label{fig:resourcesagree}Characteristics most similarly viewed as resources (lowest standard deviations).}
\end{figure}

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/challengesagree-1.pdf}
\caption{\label{fig:challengesagree}Characteristics most similarly viewed as challenges (lowest standard deviations).}
\end{figure}

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/hindrancesagree-1.pdf}
\caption{\label{fig:hindrancesagree}Characteristics most similarly viewed as hindrances (lowest standard deviations).}
\end{figure}

Figures \ref{fig:resourcesagree}, \ref{fig:challengesagree}, and \ref{fig:hindrancesagree} present the resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.\footnote{There were a few characteristics with standard deviations of ``zero'' but these were excluded from presenation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).}

As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 10 elements showing the greatest agreement still ranging in standard deviations from 1.12 to 1.19. What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 10 resource standard deviations is 0.70 to 0.88 and the range of lowest 10 challenge standard deviations is 0.79 to 0.87.

@@

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/resourcesdisagree-1.pdf}
\caption{\label{fig:resourcesdisagree}Characteristics most \emph{dis}similarly viewed as resources (highest standard deviations).}
\end{figure}

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/challengesdisagree-1.pdf}
\caption{\label{fig:challengesdisagree}Characteristics most \emph{dis}similarly viewed as challenges (highest standard deviations).}
\end{figure}

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/hindrancesdisagree-1.pdf}
\caption{\label{fig:hindrancesdisagree}Characteristics most \emph{dis}similarly viewed as hindrances (highest standard deviations).}
\end{figure}

Figures \ref{fig:resourcesdisagree}, \ref{fig:challengesdisagree}, and \ref{fig:hindrancesdisagree} present the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

Figure \ref{fig:combinegraphs} presents resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.\footnote{There were a few characteristics with standard deviations of ``zero'' but these were excluded from presenation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).} There are only 8 characteristics presented per perceived category because of limited space. All sortable ratings are available in the online resources.

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/combinegraphs-1.pdf}
\caption{\label{fig:combinegraphs}Characteristics percieved most similarly (lowest standard deviations).}
\end{figure}

As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 8 elements showing the greatest agreement still ranging in standard deviations from 1.12 to 1.16. What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 8 resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86.

@@

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/combinegraphs2-1.pdf}
\caption{\label{fig:combinegraphs2}Characteristics percieved most \emph{DIS}similarly (lowest standard deviations).}
\end{figure}

Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating).
